The Spatial Distribution of Local Group Satellites in a Cosmological Context

### 2016-08-16 paper/ms.tex
paper: intro y results

%
%Observational evidence of planes is everywhere (where we can see them). MW, M31, Centaurus A.\\
%
%Not so evident in simulations:\\
%
%Millenium II Baumgardt, Ibata, Pawlowski\\
%
%Clues Gillet está pero diferente\\
%
%Plane claims:\\
%Libeskind: preferential direction for accretion.\\
%Sawala: planes are there when baryonic physics is included.\\
%Buck: planes are easy to form at early times, when DM filaments are very thin. In high redshift galaxies galaxies, planes are everywhere.\\
%
%Other explanations: Kroupa: tidal dwarfs\\
%Fouquet\\
%
%
%
% 
%Following a bit on the claim by Sawala that barionic physics are important when looking for planes, WE look in Illustris and Elvis simulations to try and understand why barionic physics results in planar distribution of satellites.

%\subsection{Evidencias observacionales de planos:}
\noindent Since the early works of (el que libeskind dice que habló de
eso primero) and Lynden-Bell (1976), the observed anisotropic
distribution of satellite galaxies in the Local Group has been a key
point in the discussion of galaxy formation models within $\Lambda$CDM
cosmology. These pioneer papers described that the then known satellite
galaxies of the Milky May (MW) were distributed roughly following the plane
that contained the Magelanic clouds and their stellar tails. This
anisotropic distribution was further studied in the work of Pawlowski
et. al. (2012), where they included all the known MW satellite galaxies (XXX
more than in the original Lynden-Bell paper) as well as some MW globular
clusters, and found that they are all contained in what they call a
"Vast Plane Of Satellites" (VPOS). This structure is around 30kpc thick and
is perpendicular to the stellar disc of the MW galaxy. This plane of
satellites was considered a rarity until the PAndAS survey of the
Andromeda (M31) galaxy and its halo (missing reference on the survey)
provided a complete sample of the satellite galaxy population (above a
XXXX magnitude) of our neighboring galaxy, allowing their consistent distance
estimations (Conn et al. 2012). In a groundbreaking work, Ibata et
al. (2013) found that 15 out of the 30 satellites are in a planar
structure that is 15kpc thick and has an extension of 400kpc.
Additionally, from line of sight velocity measurements, they
found that the structure has an apparent coherent rotation, with the
satellites south of M31 moving away from us and those north of M31
coming towards us. This apparent organized rotation of satellite galaxies was also
statistically found to occur in diametrically opposed 
pairs of satellites from the SDSS (Ibata et al. 2014), although this
results were contested in a follow up paper by Cuatun et al. (2014).

@@

These observed planes present a challenge for current galaxy formation
models (Pawlowski et al. 2014)

%\subsection{B\'usqueda de planos en simulaciones:}
\noindent A comparison of the distribution of satellite galaxies
around Andromeda and the results of $\Lambda$CDM simulations (Bahl and
Baumgardt 2013) Encuentran planos en Millenium II.\\
A thousand shadows of Andromeda: rotating planes of satellites in the
Millennium-II cosmological simulation (Ibata et al 2013) dicen que el
paper de Bahl y Baumgardt est\'a mal y que no hay planos en millenium
II\\
Co-orbiting satellite galaxy structures are still in conflict with the
distribution of primordial dwarf galaxies (Pawlowski et al 2014)\\
Co-orbiting planes of sub-halos are similarly unlikely around paired
and isolated hosts (Pawlowski et al 2014)\\
Vast planes of satellites in a high resolution simulation of the Local
Group: comparison to Andromeda (Gillet et al 2014). finds a plnes
similar to that of M31 in Clues simulations.\\
Planes of satellite galaxies: when exceptions are the rule (Cautun et
al 2015) encuentra que 10 por ciento de los halos tienen planos
iguales o m\'as prominentes que los del LG.\\

\subsection{Posibles or\'igenes de los planos:}
\noindent Preferential accretion (Libeskind et al 20??)\\
Alignments with the cosmic web (Tempel et al 20??)\\
The vast thin plane of M31 co-rotating dwarfs: an additional fossil
signature of the M31 merger and of its considerable impact in the
whole Local Group (Hammer et al 2013) Major merger in M31-MW system
plane galaxies are tidal dwarfs (n-body simulations)\\
Kroupa tiene todo un carretazo de que las dwarfs son todas tidal
dwarfs\\
MIRAR lo que est\'a haciendo Pierre Alan Duc con tidal dwrafs porque en
una conferencia este a;o habl\'o de un posible escenario
intermedio...\\
Evidence for Early Filamentary Accretion from the Andromeda Galaxy's
Thin Plane of Satellites (Buck et al 2015)\\
Alignments between galaxies, satellite systems and haloes (Cautun et al
2016) NO LO HE LEIDO...

\subsection{Problemas con esas explicaciones:}
The Vast Polar Structure of the Milky Way and Filamentary Accretion of
Sub-Halos (Pawlowski et al 2012)\\
Paper de Collins (2013 y 2016) donde explica que no hay diferencias en
las propiedades de los on-plane y los off-plane satellites\\
Problemas con la estabilidad a largo plazo de los planos: Bowden et al
2012, Gonzales et al 2015...\\
The Plane Truth: Andromeda analog thin Planes of Satellites are not
kinematical coherent structures (Buck et al 2015)\\

\subsection{Previous studies of Local Group satellites}

\citep{2011MNRAS.411.1525L} Measure the infall direction of satellites
in a DM only simulation of one pair of LG halos in a constrained
simulation. There is a definite infall direction but it's not
quantified in terms of the cosmic web.

\citep{2012MNRAS.424...80P} Compare the kinematic structure of the MW
satellites against DM only simulation of high resolutions halos from
the Via Lactea and Aquarius projects.  Cannot find a similar kinematic
structure (i.e. the orbital poles of the MW satellites) in the
simulations.

\citep{2014MNRAS.443.1274L} Measure the infall direction of satellites
with respect to the V-web. They do it in a DM cosmological simulation
(64 Mpch, 1024 3 particles). They find that infall is done along the
e3 (i.e. filament) direction.

\citep{2015MNRAS.450.2727T} They measure the angle between satellites
and the direction defined by filaments (Bissous filament finder) to
find a signal both in SDSS and the semi-analytic galaxies in the
Millennium Simulation.

\citep{2015ApJ...799..212L} Detection of alignment of satellites along
the direction defined by filaments (velocity shear cosmic web) on the
SDSS DR7.

\citep{2016MNRAS.457.1931S} Uses the APOSTLE simulation (12 pairs) to study the
spatial anisotropy the 11 brightest satellites. The anisotropy is
quantified the reduced inertia tensor. Still the MW is more
anisotropic than all but one of the 24 halos. The analysis is not very
thorough and do not show the resulting distribution. Does not compare
the results of using DM information only.

\citep{2015ApJ...815...19P} argue that the result from
\citep{2016MNRAS.457.1931S} is a produc of using a metric that ignores
the radial position of the galaxies. They use the ELVIS suite to
compare the two analysis methods: reduced vs. full inertia tensor.

\citep{2016arXiv160501728S} Use the eagle simulation to study the
alignment of satellites with respect to the central galaxy. They find
a weak alignment. Around $20\%$ of the systems have a misalignment
angle larger than the value observed for the Milky Way. They do not
study DM only simulations and do not narrow down the signal to pairs.

\citep{2016arXiv160601516L} Using SDSS DR10 studied galaxy pairs. They find
that satellites tend to accumulate towards the companion galaxy. There
are up to $\sim 10\%$ more satellites in the space between the pair
than expected from an uniform distribution

@@

@@

In the same study they found 158 pairs with broad kinematic
characteristics, similar to the definition of our LG sample. 
This represents a reduction of a factor of $12$ from their General
Sample. 
With those numbers in mind we would expect to keep at least $4$ pairs
in the Illustris volume. 
Given that our conditions are slightly more relaxed (we do not ask for
isolation criteria from massive halos) we end up with a larger sample
size, but still consistent with the fact that LG-like pairs are
scarce.

@@

\subsection{Cosmic Web environment}

We place the pairs in our sample into the cosmic web as quantified by
the deformation tensor.
\citep{2007MNRAS.375..489H,2009MNRAS.396.1815F}.
This method computes a cartesian grid the tensor $T_{ij}$,
\begin{equation}
T_{ij} \equiv \frac{\partial^2\phi}{\partial r_i \partial r_j}
\end{equation}
%
where $\phi$ is a pseudo-gravitational potential that follows the
Poisson equation $\nabla^2\phi=-\delta$ and the $r_i$ coordinates
correspond to a cartesian system with $i=1,2,3$.

@@

\begin{figure}
\centering
\includegraphics[width=\hsize]{axratio_dark_bright.pdf}\\
\caption{Axis ratio of luminous satellites versus the axis ratio for
  dark subhalos.}
\label{fig:StreamPlaneOrbit}
\end{figure}

\begin{figure*}
\centering
\includegraphics[width=0.48\hsize]{significance_full_bright.pdf}
\includegraphics[width=0.48\hsize]{significance_lg_bright.pdf}
\caption{Significance of alignments.}
\label{fig:significance}
\end{figure*}

@@

\begin{figure}
\centering
\includegraphics[width=\hsize]{plane_width.pdf}\\
\caption{Plane width for the best planes in the luminious and dark cases.}
\label{fig:plane_width}
\end{figure}

\section{Method}
\label{Method}

@@

\section{Discussion} 
\section{Acknowledgements}
Gracias.

@@

Simulation papers:
\begin{itemize}
\item{Bahl and Baumgardt 2013 "A comparison of the distribution (...)":\\
MilleniumII and a semi-analytic model\\
Baryonic mass cut: 2.8$\times 10^4 M\odot$\\
PAndAS like field\\
With orphan galaxies: planes are common (40$\%$) but overall distribution is different from that of M31 (more radially concentrated).\\
Excluding \emph{some} orphan galaxies: overall distribution closer to M31's and finds planes.\\
Conclusion: M31 like planes are not uncommon in MilleniumII simulations. Co-rotating structures are not stable structures. Plane of M31 could be a statistical fluctuation in an otherwise more spherical distribution.\\
Simulation: Millenium II ()\\
Gas: NO\\
Resolution: sub-halos 2$\times 10^8 M\odot$ (orphan galaxies have less than 20 particles and could be tidally disrupted)\\
Number of host halos: 1511 with orphan galaxies, 112 excluding orphan galaxies (mass between 1.1$\times 10^{12} M\odot$ and 1.7$\times 10^{12} M\odot$), younger that 10 Gyr and satelites smaller than 7$\times 10^{10} M\odot$\\
Planes: yes (40$\%$ with orphan galaxies 2$\%$ without)\\
co-rotation: yes (in 2$\%$ of the halos ???)\\
Stable: No\\
Note: PAndAS data has satellites with baryonic masses down to 2.9$\times 10^{4} M\odot$ and they take that as a lower limit for their data.\\
}
\item{Ibata et al 2014 "A thousand shadows (...)":\\
MilleniumII and a semi-analytic model (Guo)\\
%Baryonic mass cut: 2.8$\times 10^4 M\odot$\\
Same analysis as in PAndAS data\\
%With orphan galaxies: planes are common (40$\%$) but overall distribution is different from that of M31 (more radially concentrated).\\
%Excluding \emph{some} orphan galaxies: overall distribution closer to M31's and finds planes.\\
Conclusion: M31 like planes are NOT common in MilleniumII simulations.\\
Simulation: Millenium II ()\\
Gas: NO\\
Resolution: sub-halos 2$\times 10^8 M\odot$ (orphan galaxies have less than 20 particles and could be tidally disrupted)\\
Number of host halos: 679 (I assume with orphan galaxies) (mass between 1.1$\times 10^{12} M\odot$ and 1.7$\times 10^{12} M\odot$, younger that 10 Gyr and satellites smaller than 7$\times 10^{10} M\odot$ they also use LG upper mass limit, and an isolation criteria).\\
Planes: no (with orphan galaxies only 0.04$\%$ of the system fulfill the thinness, extension and co-rotation criteria, and NONE does if orphans are not included. If co-rotation is not included then $2\%$ fulfill the thinness and extension criteria)\\
co-rotation: only 0.04$\%$ with orphans and NONE without orphans\\
Note: they use the 679 host halos and study them from different viewing angles\\
}
\item{Pawlowski et al 2014 "Co-orbitingsatellite galaxy structures are still in conflict with (...)":\\
MilleniumII and a semi-analytic model (Guo)\\
%Baryonic mass cut: 2.8$\times 10^4 M\odot$\\
Same analysis as in PAndAS data\\
Same analysis as in Wang et al. 2013\\
%With orphan galaxies: planes are common (40$\%$) but overall distribution is different from that of M31 (more radially concentrated).\\
%Excluding \emph{some} orphan galaxies: overall distribution closer to M31's and finds planes.\\
Conclusion: M31 and MW like planes are NOT common in MilleniumII simulations.\\
Simulation: Millenium II ()\\
Gas: NO\\
Resolution: sub-halos 2$\times 10^8 M\odot$ (orphan galaxies have less than 20 particles and could be tidally disrupted)\\
Number of host halos:  1825 (mass between 1.1$\times 10^{12} M\odot$ and 1.7$\times 10^{12} M\odot$, younger that 10 Gyr and satellites smaller than 7$\times 10^{10} M\odot$ they also use LG upper mass limit, and an isolation criteria).\\
Planes: no (M31: 0.09$\%$ fulfill the thinness, extension and co-rotation criteria. MW: 0.2$\%$)\\
Note: they use the host halos and study them from different viewing angles so they end up with 15000 samples. They always consider orphan galaxies for comparison purposes. For one test they randomize the sample and find M31 like planes in only 0.002 per cent of the cases and MW like planes in 0.06$\%$ of the cases.\\
MIRAR Wang et al. 2013 que busca MWlike planes en MilleniumII y encuentra que $13\%$ de los halos tienen planos
}
\item{Cautun et al. 2015 "Planes of satellite galaxies: when exceptions are the rule":\\
MilleniumII and a semi-analytic model (Guo 2013)\\
CoCo and a semi-analytic model (Guo 2015)\\
%Baryonic mass cut: 2.8$\times 10^4 M\odot$\\
Conclusion: planar structures are very common in $\Lambda$CDM (10$\%$)\\
Simulation 1: Millenium IIi rescaled to WMAP\\
Simulation 2: CoCo (Higher resolution than MilleniumII)\\
Gas: NO\\
Resolution 1: sub-halos 2$\times 10^8 M\odot$ (orphan galaxies have less than 20 particles and could be tidally disrupted)\\
Number of host halos:  2849 (MilleniumII) and 63 8COCO halos) (selection criteria: "we adopted a broader mass range to account for the large uncertainty in the mass measurements and also for possible systematic effects").\\
Resolution 2: sub-halos $\approx$ 2$\times 10^6 M\odot$ (75 times higher mass resolution
and four times better spatial resolution)\\
Planes: yes (10$\%$)\\
Note: They found a great variety of plane and the M31 plane lies in general within the scatter of the simulated planes however it seem to have an "unusually large radial extent".\\
Note 2: they find that each halos has a different planar configuration showing that the low incidence of the M31 plane is not in contradiction with simulations. This contradicts the Pawlowski et al. 2014 conclusions}

\item{Sawala et al. 2014 "The chosen few: the low mass halos that host faint galaxies":\\
Conclusion: Some "effects make dwarf galaxies highly biased
tracers of the underlying dark matter distribution."\\
Simulation: 12 cosmological volumes as zoom" simulations
extracted from the Dove simulation. They require that each box has to
have two halos (MW and M31 like)\\
Gas: Yes (they also compare their results with DM only simulations)\\
Resolution : sub-halos 1 $\times 10^7 M\odot$\\
Number of host halos:  2 times 12 (pairs of galaxies).\\
Planes: They do not look for them\\}

\item{Libeskind et al. 2012 "The universal nature of subhalo accretion":\\
Conclusion: "the preferential infall of subhaloes is effectively universal
in the sense that its always aligned with the axis of weakest collapse
of the velocity shear tensor. It is the same shear tensor that
dictates the structure of the cosmic web and hence the shear field
emerges as the key factor that governs the local anisotropic pattern
of structure formation."\\
Simulation:DM-only N-body simulation of 10243 particles in a
64h$^{-1}$ Mpc box.\\
Gas: NO\\
Resolution : particle 1.89 $\times 10^7 h^{-1} M\odot$\\
Resolution : halos 1$\times 10^9 h^{-1} M\odot$\\
Number of host halos:  not mentioned.\\
Planes: They do not look for them. They look and find preferential
directions for accretion\\}

\item{Libeskind et al. 2015 "Planes of satellite galaxies and the
cosmic web":\\
Conclusion:"The analysis reveals that the Local Group and Centaurus A
reside in a filament stretched by the Virgo cluster and compressed by
the expansion of the Local Void. Four out of five thin planes of
satellite galaxies are indeed closely aligned with the axis of
compression induced by the Local Void. (...) "\\ 
Simulation: Observational paper uses the cosmic flow data set.\\
Gas: No aplica\\
\\}

\item{Tempel et al. 2015 "The alignment of satellite galaxies and
cosmic filaments: observations and simulations":\\
Conclusion:"A statistically significant alignment between satellite
galaxy position and filament axis in observations is confirmed. We
find a qualitatively compatible alignments by examining satellites and
filaments similarly identified in the Millennium simulation,
semi-analytical galaxy catalogue. We also examine the dependence of
the alignment strength on galaxy properties such as colour, magnitude
and (relative) satellite magnitude, finding that the alignment is
strongest for the reddest and brightest central and satellite
galaxies. "\\ 
Simulation: MilleniumII compared to Observational data (SDSS).\\
Gas: No\\
Alignments: yes both in simulations and in observations\\
Note: they make a statistical analysis of alignments in projected
data.}

>>>>

Since the early works of (el que libeskind dice que habló de
eso primero) and \cite{1976MNRAS.174..695L}, the observed anisotropic
distribution of satellite galaxies in the Local Group has been a key
point in the discussion of galaxy formation models within $\Lambda$CDM
cosmology. These pioneer papers described that the then known satellite
galaxies of the Milky May (MW) were distributed roughly following the plane
that contained the Magelanic clouds and their stellar tails. This
anisotropic distribution was further studied in the work of \cite{}Pawlowski
et. al. (2012), where they included all the known MW satellite galaxies (XXX
more than in the original Lynden-Bell paper) as well as some MW globular
clusters, and found that they are all contained in what they call a
"Vast Plane Of Satellites" (VPOS). This structure is around 30kpc thick and
is perpendicular to the stellar disc of the MW galaxy. This plane of
satellites was considered a rarity until the PAndAS survey of the
Andromeda (M31) galaxy and its halo (missing reference on the survey)
provided a complete sample of the satellite galaxy population (above a
XXXX magnitude) of our neighboring galaxy, allowing their consistent distance
estimations (Conn et al. 2012). In a groundbreaking work, Ibata et
al. (2013) found that 15 out of the 30 satellites are in a planar
structure that is 15kpc thick and has an extension of 400kpc.
Additionally, from line of sight velocity measurements, they
found that the structure has an apparent coherent rotation, with the
satellites south of M31 moving away from us and those north of M31
coming towards us. This apparent organized rotation of satellite galaxies was also
statistically found to occur in diametrically opposed 
pairs of satellites from the SDSS (Ibata et al. 2014), although this
results were contested in a follow up paper by Cuatun et al. (2014).

@@

These observed planes and their apparent co-rotation seem to challenge
current galaxy formation models (Pawlowski et al. 2014).
\cite{2012MNRAS.424...80P} compared the kinematic structure of the MW
satellites against DM only simulation of high resolution halos from
the Via Lactea and Aquarius projects and could not find find a similar
kinematic structure (i.e. the orbital poles of the MW satellites) in
the simulations. Additionally, a few months after the discovery of the
M31 plane of satellites, Bahl and Baumgardt (2013) looked for similar
structures in the MilleniummII dark matter only cosmological
simulations, and found that planar structures are common (they found
them in around 2 per cent of host halos). Nevertheless these results
were contradicted by the works of Ibata el al. (2014) and Pawlowski et
al. (2014) who, analyzing the same cosmological simulations with
methods closer to those used to analyze the observational data, found
that planar structures such as that observed in M31 are extremely rare
(less than 0.02 per cent or 0.004 per cent respectively). But
satellite galaxies are not particularly good tracers of the underlying
dark matter structure (Sawala 2014), and indeed anisotropic
distributions of the satellites have been found in the APOSTOLE
simulations that include baryonic physics \citep{2016MNRAS.457.1931S},
although the Milky Way remains an extreme case. These results were
contested by \cite{2015ApJ...815...19P} who claim that the
anisotropies found are a product of using a metric that ignores the
radial position of the galaxies. %Sawalla et al. 2014
In CLUES, a high resolution constrained Local Group simulation,
Gillet et al. (2015) found M31-like planes but again, the observed M31 plane
remains an extreme case, and this seems to be corroborated by Cautun
et al. (2015), who, despite finding a great variety of planes in
simulations remarks that the observed M31 plane has an "unusually large
radial extent".\\

In addition to these plane-finding efforts in cosmological simulations,
many works have focused on the possible formation processes that led
to planar structures and on the alignments  of these structures with
the cosmic web. In a pioneer work \cite{2011MNRAS.411.1525L} measured
the infall direction of satellites in a DM only constrained simulation of one pair
of LG halos and found that there is a definite infall direction. 
% but it's not quantified in terms of the cosmic web.
Using cosmological dark matter only simulations
\cite{2014MNRAS.443.1274L} showed that the preferential infall
direction was along cosmic filaments, result that was also obtained by 
\cite{2015ApJ...799..212L}. This result was further
confirmed by \cite{2015MNRAS.450.2727T}, who measure the angle between
satellites and the direction defined by filaments (Bissous filament
finder) to find a signal both in the SDSS galaxy catalog and in the
semi-analytic galaxies in the Millennium Simulation. Additionally, 
an analysis of the cosmic flow data set by Libeskind et al. (2015) 
reveals that four out of the fives satellite planes observed in the 
Local Group are aligned with a filament. 
Additionally, \cite{2016arXiv160601516L} use the SDSS DR10 catalog to study galaxy pairs and find that satellites tend to accumulate towards the companion galaxy: There
are up to $\sim 10\%$ more satellites in the space between the pair
than expected from an uniform distribution.

Early filamentary accretion has been proposed as the formation mechanism for the Andromeda thin plane of satellites (Buck et al 2015), with early formed galaxies accreting their mass via cold thin filaments. 
This formation mechanism results naturally in thin planes, but a follow up work shows that these are not kinematically coherent structures (Buck et al. 2015). These results are from dark matter only simulations, so it would be interesting to see if they still hold for simulations that include baryonic physics, since it was shown by Gonzales et al 2015 that satellites acrreted via filaments are destroyed faster than those that are not.

In a more general numerical study,   
\cite{2016arXiv160501728S} use the eagle simulation to study the
alignment of satellites with respect to the central galaxy. They find
a weak alignment. Around $20\%$ of the systems have a misalignment
angle larger than the value observed for the Milky Way.

Planes in simulations tend to be transient structures (not
kinematically coherent) and that poses two problems: one is why do we
see planes in all the galaxies were we can actually make the
measurements if they are transient? Problem with the MW plane for which
some of the dwarfs have proper motion measurements. Another problem:
explicación de Buck 2015 sería rara entonces...

@@

In this work we use the publicly available results from the Illustris
simulation (Vogelsberger et al. 2014). This cosmological simulation, performed using
the quasi-Lagrangian code AREPO, follows the coupled evolution of dark
matter and gas, and includes parametrizations to account for the effects of
gas cooling, photoionization, star formation, stellar feedback, black
hole and super massive black hole feedback. Vogelsberger et al. 2014 use a $75 Mpc/h$
simulation box, with $\Lambda$CDM cosmology initial conditions
starting at a redshift $z=127$ and consistent with WMAP-9 measurments.

@@

In the same study they found 158 pairs with broad kinematic
characteristics, similar to the definition of our LG sample. 
This represents a reduction of a factor of $12$ from their General
Sample. 
With those numbers in mind we would expect to keep at least $4$ pairs
in the Illustris volume. 
Given that our conditions are slightly more relaxed (we do not ask for
isolation criteria from massive halos) we end up with a larger sample
size, but still consistent with the fact that LG-like pairs are
scarce.  
%no me es muy claro este ultimo parrafo. En nuestros samples pasamos de 49 a 24 (o sea se redujo en un factor 2 en vez de un factor 12)

@@

\subsection{Cosmic Web environment}
%me parece que la palabra "place" puede ser confusa. 
We place the pairs in our sample into the cosmic web as quantified by
the deformation tensor.
\citep{2007MNRAS.375..489H,2009MNRAS.396.1815F}.
This method computes a cartesian grid the tensor $T_{ij}$,
\begin{equation}
T_{ij} \equiv \frac{\partial^2\phi}{\partial r_i \partial r_j}
\end{equation}
%
where $\phi$ is a pseudo-gravitational potential that follows the
Poisson equation $\nabla^2\phi=-\delta$ and the $r_i$ coordinates
correspond to a cartesian system with $i=1,2,3$.

@@

\subsection{Characterization of spatial distributions}
\label{Method}
In this paper, our aim is to study alignments: of the
satellite population with the cosmic web, of the dark matter halos
with the axis that unites them, etc... To do this, we fitted a triaxial spheroid to both the satellite (bright) and the dark matter (dark) subhalo distributions, to get both their semi-major and semi-minor axis.
With this geometrical information we can study the alignments of the two distributions with the cosmic web, and also with the vector that unites the halo pair that host these substructures. %Jaime, falta el plot de alineaciones con la cosmic web

Some papers claim that once baryonic physics is included more planar distributions are found.
First we investigate if there is a difference in the bright and dark distribution in terms of their flatness.
In Figure \ref{fig:StreamPlaneOrbit} we can see that indeed the bright distribution is flatter than the dark distribution.
\begin{figure}
\centering
\includegraphics[width=\hsize]{axratio_dark_bright.pdf}\\
\caption{Axis ratio of luminous satellites versus the axis ratio for
  dark subhalos.}
\label{fig:StreamPlaneOrbit}
\end{figure}

We then try to fit planes to both the dark and bright distributions in order to test if it is indeed easier to find thinner planes in the bright distribution. 
We find that the bright planes are thinner.
\begin{figure}
\centering
\includegraphics[width=\hsize]{plane_width.pdf}\\
\caption{Plane width for the best planes in the luminious and dark cases.}
\label{fig:plane_width}
\end{figure}
But is there a physical reason for that? Apparently not, since the thinness of the fitted planes seems to be only due to number of objects: number of bright satellites is smaller than of dark sub-halos and that results naturally in thinner fitted planes.
%pregunta para Jaime: en tu código dark quiere decir dm only subhalos o todos los subhalos (dm only y bright)?
%podríamos hacer como un test extra el plot que yo tenía en mis plot de antes, que es cojer al azar entre los dark un numero de subhalos igual al de bright y ver los anchos de los planos.

A second test is to look if there is any evidence of alignments between the distribution of satellites and the axis that unites the main halos that form the pair.

@@

\begin{figure*}
\centering
\includegraphics[width=0.48\hsize]{significance_full_bright.pdf}
\includegraphics[width=0.48\hsize]{significance_lg_bright.pdf}
\caption{Significance of alignments for both samples.}
\label{fig:significance}
\end{figure*}

@@

\section{Discussion}
Difference between bright and dark distributions are only due to number.\\
We find significant alignments between distributions and H1H2 axis. But this alignments are the opposite as the one observed for the Local Group!!!

\section{Acknowledgements}
Gracias.

@@

%Simulation papers:
%%\item {ya}
%%\item{Bahl and Baumgardt 2013 "A comparison of the distribution (...)":\\
%%MilleniumII and a semi-analytic model\\
%%Baryonic mass cut: 2.8$\times 10^4 M\odot$\\
%%PAndAS like field\\
%%With orphan galaxies: planes are common (40$\%$) but overall distribution is different from that of M31 (more radially concentrated).\\
%%Excluding \emph{some} orphan galaxies: overall distribution closer to M31's and finds planes.\\
%%Conclusion: M31 like planes are not uncommon in MilleniumII simulations. Co-rotating structures are not stable structures. Plane of M31 could be a statistical fluctuation in an otherwise more spherical distribution.\\
%%Simulation: Millenium II ()\\
%%Gas: NO\\
%%Resolution: sub-halos 2$\times 10^8 M\odot$ (orphan galaxies have less than 20 particles and could be tidally disrupted)\\
%%Number of host halos: 1511 with orphan galaxies, 112 excluding orphan galaxies (mass between 1.1$\times 10^{12} M\odot$ and 1.7$\times 10^{12} M\odot$), younger that 10 Gyr and satelites smaller than 7$\times 10^{10} M\odot$\\
%%Planes: yes (40$\%$ with orphan galaxies 2$\%$ without)\\
%%co-rotation: yes (in 2$\%$ of the halos ???)\\
%%Stable: No\\
%%Note: PAndAS data has satellites with baryonic masses down to 2.9$\times 10^{4} M\odot$ and they take that as a lower limit for their data.\\
%%}
%%\item {ya}
%%\item{Ibata et al 2014 "A thousand shadows (...)":\\
%%MilleniumII and a semi-analytic model (Guo)\\
%%%Baryonic mass cut: 2.8$\times 10^4 M\odot$\\
%%Same analysis as in PAndAS data\\
%%%With orphan galaxies: planes are common (40$\%$) but overall distribution is different from that of M31 (more radially concentrated).\\
%%%Excluding \emph{some} orphan galaxies: overall distribution closer to M31's and finds planes.\\
%%Conclusion: M31 like planes are NOT common in MilleniumII simulations.\\
%%Simulation: Millenium II ()\\
%%Gas: NO\\
%%Resolution: sub-halos 2$\times 10^8 M\odot$ (orphan galaxies have less than 20 particles and could be tidally disrupted)\\
%%Number of host halos: 679 (I assume with orphan galaxies) (mass between 1.1$\times 10^{12} M\odot$ and 1.7$\times 10^{12} M\odot$, younger that 10 Gyr and satellites smaller than 7$\times 10^{10} M\odot$ they also use LG upper mass limit, and an isolation criteria).\\
%%Planes: no (with orphan galaxies only 0.04$\%$ of the system fulfill the thinness, extension and co-rotation criteria, and NONE does if orphans are not included. If co-rotation is not included then $2\%$ fulfill the thinness and extension criteria)\\
%%co-rotation: only 0.04$\%$ with orphans and NONE without orphans\\
%%Note: they use the 679 host halos and study them from different viewing angles\\
%%}
%%\item {ya}
%%\item{Pawlowski et al 2014 "Co-orbitingsatellite galaxy structures are still in conflict with (...)":\\
%%MilleniumII and a semi-analytic model (Guo)\\
%%%Baryonic mass cut: 2.8$\times 10^4 M\odot$\\
%%Same analysis as in PAndAS data\\
%%Same analysis as in Wang et al. 2013\\
%%%With orphan galaxies: planes are common (40$\%$) but overall distribution is different from that of M31 (more radially concentrated).\\
%%%Excluding \emph{some} orphan galaxies: overall distribution closer to M31's and finds planes.\\
%%Conclusion: M31 and MW like planes are NOT common in MilleniumII simulations.\\
%%Simulation: Millenium II ()\\
%%Gas: NO\\
%%Resolution: sub-halos 2$\times 10^8 M\odot$ (orphan galaxies have less than 20 particles and could be tidally disrupted)\\
%%Number of host halos:  1825 (mass between 1.1$\times 10^{12} M\odot$ and 1.7$\times 10^{12} M\odot$, younger that 10 Gyr and satellites smaller than 7$\times 10^{10} M\odot$ they also use LG upper mass limit, and an isolation criteria).\\
%%Planes: no (M31: 0.09$\%$ fulfill the thinness, extension and co-rotation criteria. MW: 0.2$\%$)\\
%%Note: they use the host halos and study them from different viewing angles so they end up with 15000 samples. They always consider orphan galaxies for comparison purposes. For one test they randomize the sample and find M31 like planes in only 0.002 per cent of the cases and MW like planes in 0.06$\%$ of the cases.\\
%%MIRAR Wang et al. 2013 que busca MW-like planes en MilleniumII y encuentra que $13\%$ de los halos tienen planos
%%}
%%\item {ya}
%%\item{Cautun et al. 2015 "Planes of satellite galaxies: when exceptions are the rule":\\
%%MilleniumII and a semi-analytic model (Guo 2013)\\
%%CoCo and a semi-analytic model (Guo 2015)\\
%%%Baryonic mass cut: 2.8$\times 10^4 M\odot$\\
%%Conclusion: planar structures are very common in $\Lambda$CDM (10$\%$)\\
%%Simulation 1: Millenium IIi rescaled to WMAP\\
%%Simulation 2: CoCo (Higher resolution than MilleniumII)\\
%%Gas: NO\\
%%Resolution 1: sub-halos 2$\times 10^8 M\odot$ (orphan galaxies have less than 20 particles and could be tidally disrupted)\\
%%Number of host halos:  2849 (MilleniumII) and 63 8COCO halos) (selection criteria: "we adopted a broader mass range to account for the large uncertainty in the mass measurements and also for possible systematic effects").\\
%%Resolution 2: sub-halos $\approx$ 2$\times 10^6 M\odot$ (75 times higher mass resolution
%%and four times better spatial resolution)\\
%%Planes: yes (10$\%$)\\
%%Note: They found a great variety of plane and the M31 plane lies in general within the scatter of the simulated planes however it seem to have an "unusually large radial extent".\\
%%Note 2: they find that each halos has a different planar configuration showing that the low incidence of the M31 plane is not in contradiction with simulations. This contradicts the Pawlowski et al. 2014 conclusions}
%%
%%\item{Sawala et al. 2014 "The chosen few: the low mass halos that host faint galaxies":\\
%%Conclusion: Some "effects make dwarf galaxies highly biased
%%tracers of the underlying dark matter distribution."\\
%%Simulation: 12 cosmological volumes as zoom" simulations
%%extracted from the Dove simulation. They require that each box has to
%%have two halos (MW and M31 like)\\
%%Gas: Yes (they also compare their results with DM only simulations)\\
%%Resolution : sub-halos 1 $\times 10^7 M\odot$\\
%%Number of host halos:  2 times 12 (pairs of galaxies).\\
%%Planes: They do not look for them\\}

%                            \begin{itemize}
%                            \item{Libeskind et al. 2012 "The universal nature of subhalo accretion":\\
%                            Conclusion: "the preferential infall of subhaloes is effectively universal
%                            in the sense that its always aligned with the axis of weakest collapse
%                            of the velocity shear tensor. It is the same shear tensor that
%                            dictates the structure of the cosmic web and hence the shear field
%                            emerges as the key factor that governs the local anisotropic pattern
%                            of structure formation."\\
%                            Simulation:DM-only N-body simulation of 10243 particles in a
%                            64h$^{-1}$ Mpc box.\\
%                            Gas: NO\\
%                            Resolution : particle 1.89 $\times 10^7 h^{-1} M\odot$\\
%                            Resolution : halos 1$\times 10^9 h^{-1} M\odot$\\
%                            Number of host halos:  not mentioned.\\
%                            Planes: They do not look for them. They look and find preferential
%                            directions for accretion\\}
%                            
%                            %%\item{Libeskind et al. 2015 "Planes of satellite galaxies and the
%                            %%cosmic web":\\
%                            %%Conclusion:"The analysis reveals that the Local Group and Centaurus A
%                            %%reside in a filament stretched by the Virgo cluster and compressed by
%                            %%the expansion of the Local Void. Four out of five thin planes of
%                            %%satellite galaxies are indeed closely aligned with the axis of
%                            %%compression induced by the Local Void. (...) "\\ 
%                            %%Simulation: Observational paper uses the cosmic flow data set.\\
%                            %%Gas: No aplica\\
%                            %%\\}
%                            
%                            %%\item{Tempel et al. 2015 "The alignment of satellite galaxies and
%                            %%cosmic filaments: observations and simulations":\\
%                            %%Conclusion:"A statistically significant alignment between satellite
%                            %%galaxy position and filament axis in observations is confirmed. We
%                            %%find a qualitatively compatible alignments by examining satellites and
%                            %%filaments similarly identified in the Millennium simulation,
%                            %%semi-analytical galaxy catalogue. We also examine the dependence of
%                            %%the alignment strength on galaxy properties such as colour, magnitude
%                            %%and (relative) satellite magnitude, finding that the alignment is
%                            %%strongest for the reddest and brightest central and satellite
%                            %%galaxies. "\\ 
%                            %%Simulation: MilleniumII compared to Observational data (SDSS).\\
